Corpus Analysis

### 2020-08-27 inst/analysis/corpus-stage2.Rmd
Fix forgotten kaggle stage2

package_programs <-
  left_join(
    package_programs, 
    transmute(package_programs_errors, error=paste(source, message, call), file), 
    by="file"
  ) %>%
  mutate(
    success=
      type %in% c("examples", "tests", "vignettes") & 
      !is.na(code) &
      !is.na(runtime) &
      code > 0 &
      is.na(error)
  )

>>>>

package_programs <-
  left_join(
    package_programs,
    if (nrow(package_programs_errors) > 0) {
      transmute(package_programs_errors, error=paste(source, message, call), file)
    } else {
      transmute(package_programs, error=NA, file)
    }, 
    by="file"
  ) %>%
  mutate(
    success=
      type %in% c("examples", "tests", "vignettes") & 
      !is.na(code) &
      !is.na(runtime) &
      code > 0 &
      is.na(error)
  )
